### 2020-07-22 paper/conclusion.tex
Before submitting to Annals
After Andrei's review

All absorbing materials provide an adequate shutdown margin for the SD-TMSR 
core that initially loaded with $^{233}$U and reactor-grade Pu. However, the 
shutdown margins for TRU case are negative or slightly positive (in B$_4$C-90 
case).

The amplification factor (A$_{CRi}$) results show that the CSD, SSD, CSD inner ring, and SSD1 are slightly amplified due to the anti-shadowing effects. The strongest anti-shadowing effect has observed in SSD4 and CSD9 clusters that are located at the boundary between the core zones with different moderator-to-fuel ratio.

>>>>

All absorbing materials provide an adequate shutdown margin for the SD-TMSR 
core that initially loaded with $^{233}$U and reactor-grade Pu. However, the 
shutdown margins for TRU case are negative or slightly positive (in B$_4$C-90 
case). Increasing the number of SSD clusters would provide a sufficient positive SDM for the TRU case.

The amplification factor (A$_{CRi}$) results show that the CSD, SSD, CSD inner ring, and SSD1 are slightly amplified due to the anti-shadowing effects. The strongest anti-shadowing effect has observed in SSD4 and CSD9 clusters that are located at the boundary between the core zones with different moderator-to-fuel ratios. This happened because fewer clusters surround the SSD4 and CSD9 clusters compared with other clusters located in the inner zone of the SD-TMSR.

### 2020-07-22 paper/results.tex
After Andrei's review

The SERPENT-2 is used to obtain all presented results.
We use the ENDF-VII.0 cross section library for all calculations in the current work. The statistical error in $k_{eff}$ is $\leq$ $25$ $pcm$.
The initial calculation state of a full 3D model of the SD-TMSR is identified by normal operation 
conditions (see Table~\ref{tab:table1}) and fully withdrawn control rod 
clusters. 
The obtained results including excess reactivity, control rod 
worth, shutdown margin, interference effects (shadowing effects), etc. are discussed below.

@@

The excess reactivity $\rho$$_e$ is calculated by using equation~\ref{Equ:1} at zero burnup (steady-state 
calculation), when all control rods (CRs) are fully withdrawn. The $\rho_e$ for $^{233}$U, 
reactor-grade Pu, and TRU used as initial fissile material are listed in Table~\ref{tab:excess}.
For $^{233}$U case \cite{ashraf2020Strategies} the maximum observed excess reactivity is $4.27\pm0.01$ $\$$ during 60 effective full-power years (EFPY) of operation (see Figure~\ref{fig:keff_25} (at $\approx$ 8 EFPY)).
The proposed reactivity control system must compensate such reactivity at startup and during burnup.

@@

The amplification factor (A$_{CRi}$) results show that the CSD, SSD, CSD inner 
ring, and SSD1 are slightly amplified due to the anti-shadowing effects. The 
anti-shadowing is observed when the combined rod worth is greater than the sum 
of the individual worths. As listed in Tables~\ref{tab:worth} and ~\ref{tab:table25}, the strongest anti-shadowing effect occurred in 
SSD4 and CSD9 clusters that are located at the boundary between the core zones 
with different moderator-to-fuel ratios. This can be attributed to the fact that the SSD4 and CSD9 clusters are surrounded by fewer clusters compared with other clusters located in the inner zone of the SD-TMSR (see Figure~\ref{fig:core_25}). Consequently, low interference between these SSD4 and CSD9 clusters and other surrounding clusters is observed. The obtained results show a negligible relationship between the absorbing material type and the interference between the CR clusters (i.e., the A$_{CRi}$).

>>>>

We employed the SERPENT-2 Monte Carlo code to calculate all parameters herein.
We used the ENDF/B-VII.0 \cite{CHADWICK20062931} cross section library for all calculations in the current work. The statistical error in $k_{eff}$ is $\leq$ $25$ $pcm$.
The initial calculation state of a full 3D model of the SD-TMSR is identified by normal operation 
conditions (see Table~\ref{tab:table1}) and fully withdrawn control rod 
clusters. 
The obtained results including excess reactivity, control rod 
worth, shutdown margin, interference effects (shadowing effects), etc. are discussed below.

@@

The excess reactivity $\rho$$_e$ is calculated by using equation~\ref{Equ:1} at zero burnup (steady-state 
calculation), when all control rods (CRs) are fully withdrawn. The $\rho_e$ for $^{233}$U, 
reactor-grade Pu, and TRU used as initial fissile material are listed in Table~\ref{tab:excess}.
For $^{233}$U case \cite{ashraf2020Strategies} the maximum observed excess reactivity is $4.27\pm0.01$ $\$$ during 60 effective full-power years (EFPY) of operation (see Figure~\ref{fig:keff_25} after $\approx$ 8 EFPY of operation).
The proposed reactivity control system must compensate such reactivity at startup and during burnup.

@@

The amplification factor (A$_{CRi}$) results show that the CSD, SSD, CSD inner 
ring, and SSD1 are slightly amplified due to the anti-shadowing effects. The 
anti-shadowing is observed when the combined rod worth is greater than the sum 
of the individual worths. As listed in Tables~\ref{tab:worth} and ~\ref{tab:table25}, the strongest anti-shadowing effect occurred in 
SSD4 and CSD9 clusters that are located at the boundary between the core zones 
with different moderator-to-fuel ratios. This happened because fewer clusters surround the SSD4 and CSD9 clusters compared with other clusters located in the inner zone of the SD-TMSR (see Figure~\ref{fig:core_25}). Consequently, low interference between these SSD4 and CSD9 clusters and other surrounding clusters is observed. The obtained results show a negligible relationship between the absorbing material type and the interference between the CR clusters (i.e., the A$_{CRi}$).
